Randomized trace estimation for parameter-dependent matrices applied to spectral density approximation

### 2024-07-05 paper/re-pro-badge.tex

This document, along with all included plots and tables, was generated from commit \href{https://github.com/FMatti/Rand-TRACE/tree/b1d98c9}{b1d98c9} at \url{https://github.com/FMatti/Rand-TRACE} on 2024-07-01 at 10:20:08 UTC.

>>>>

This document, along with all included plots and tables, was generated from commit \href{https://github.com/FMatti/Rand-TRACE/tree/a3299bf}{a3299bf} at \url{https://github.com/FMatti/Rand-TRACE} on 2024-07-04 at 14:51:50 UTC.
